Single cell resolution landscape of equine peripheral blood mononuclear cells reveals diverse cell types including T-bet+ B cells.

### 2020-12-14 analysis/paper/paper.Rmd
update paper.rmd to use curl command to pull ESAT processed gene-cell matrices from GEO

```{r Reading in the ESAT processed gene-cell matrices, include=FALSE}
## Pull counts matrices directly from GEO
#tmpdir <- tempdir()
#url <- "https://www.ncbi.nlm.nih.gov/geo/download/?acc=GSE148416&format=file"
#file <- basename(url)
#download.file(url, file)
#untar(file, compressed = "gzip", exdir = tmpdir)
## Extract and unzip gene-cell matrices only
tmpdir <- "../data/raw_data/GSE148416_RAW/"
gz.files <- lapply(list.files(path = tmpdir, full.names = T, pattern = "GSM"), gzfile)
counts <- lapply(gz.files, read.table, sep = "\t")
names(counts) <- strsplit(list.files(tmpdir), split = "_") %>% sapply("[[", 2)
counts <- lapply(counts, function(x) {
  colnames(x) <- gsub(x = colnames(x), pattern = ".*\\.", replacement = "")
  return(x)
})
```

>>>>

```{r Reading in the ESAT processed gene-cell matrices, include=FALSE}
## Pull counts matrices directly from GEO
tmpdir <- tempdir()
url <- "https://www.ncbi.nlm.nih.gov/geo/download/?acc=GSE148416&format=file"
file <- basename(url)
download.file(url, file)
untar(file, compressed = "gzip", exdir = tmpdir)
## Extract and unzip gene-cell matrices only
gz.files <- lapply(list.files(path = tmpdir, full.names = T, pattern = "GSM"), gzfile)
counts <- lapply(gz.files, read.table, sep = "\t")
names(counts) <- strsplit(list.files(tmpdir), split = "_") %>% sapply("[[", 2)
counts <- lapply(counts, function(x) {
  colnames(x) <- gsub(x = colnames(x), pattern = ".*\\.", replacement = "")
  return(x)
})
```
